---
title: "Midpoint Deliverable"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
source("scripts/chart4.R")
```

## Introduction

For the domain of our project we are looking at Eduction with a focus on the financial background of schools over the years and how it has changed in response to different events and/or changes between geographical location or point in time.

## Summary

Some general information from this dataset ...

## Table of aggregated data

This table is grouped by ...

## Chart 1

This chart shows ... We decided to go with a ... chart because ...

## Chart 2

This chart shows ... We decided to go with a ... chart because ...

## Chart 3

This chart shows ... We decided to go with a ... chart because ...

## Chart 4

This chart shows the relationship between Federal, State, and Local funding for the country over the years.
Blue represents Federal funding
Red represents State funding
Green represents Local funding
```{r echo=FALSE}
generateTrends("data/funding/prepped/aggregate.csv")
```



