---
title: "Midpoint Deliverable"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
source("scripts/chart1.R")
source("scripts/chart4.R")
source("scripts/chart3.R")
```

## Introduction

For the domain of our project we are looking at Eduction with a focus on the financial background of schools over the years and how it has changed in response to different events and/or changes between geographical location or point in time.

## Summary

Some general information from this dataset ...

## Table of aggregated data

This table is grouped by ...

## Chart 1

This chart shows the progression of funding for schools since 1995 through 2015. We decided to go with a bar chart because of the simplicity of the informaiton that this chart would be showing.

```{r echo=FALSE}
generateTotalFunding("data/funding/prepped/aggregate.csv")
```

## Education Funding Surplus

This chart shows the surplus in 2000 education funds for mainland U.S. states. We decided to go with a choropleth map because it gives a clear visualization of each state, allowing us to see trends over the country as a whole based on location. In addition, the color gradient makes it easy to see the range of surplus amount from positive to negative very easily at a glance.

```{r echo=FALSE}
surplus_map("data/funding/prepped/aggregate.csv", 2000)
```

## Chart 3

This chart shows the difference between total revenue and expenditures for all schools grouped by year.
The red bars represent the amount of debt and the green the amount of surplus.

```{r echo=FALSE}
divergingMap("scripts/summaryTable.R")
```

## Chart 4

This chart shows the relationship between Federal, State, and Local funding for the country over the years.
Blue represents Federal funding
Red represents State funding
Green represents Local funding
```{r echo=FALSE}
generateTrends("data/funding/prepped/aggregate.csv")
```



