---
title: "Midpoint Deliverable"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
source("scripts/summaryTable.R")
source("scripts/chart1.R")
source("scripts/chart2.R")
source("scripts/chart3.R")
source("scripts/chart4.R")
```

## Introduction

For this project, we are looking at the domain of education with a focus on the financial characteristics of schools over the past twenty years and how they has differ over time and geographic location.

To look into this, we are using compiled datasets from the U.S. Census Bureau as authorized by Title 13, United States Code, Section 161 and 182. Under this authorization, we are able to access surveys of every school in the United States, including Washington D.C., in order to collect information on education finance data such as revenue, expenditure, debt, and assets of elementary and secondary public school systems.

We have used this information to provide a general overview and learn about aspects of it including [chart 1], [chart 2], [chart 3], and [chart 4].

## Summary

Some general information from this dataset ...

## Table of Aggregated Data

This table is grouped by ...

```{r aggregated_data, include=FALSE}

```

## USA Education Funding Over Time

This chart shows the progression of funding for schools since 1995 through 2015. We decided to go with a bar chart because of the simplicity of the informaiton that this chart would be showing.

```{r chart_1, echo=FALSE}
generateTotalFunding("data/funding/prepped/aggregate.csv")
```

## Education Funding Surplus

This chart shows the surplus in 2000 education funds for mainland U.S. states. We decided to go with a choropleth map because it gives a clear visualization of each state, also allowing us to see trends over the country as a whole based on location. In addition, the color gradient makes it easy to see the range of surplus amount among states from positive to negative very easily at a glance.

```{r chart_2, echo=FALSE}
surplus_map("data/funding/prepped/aggregate.csv", 2000)
```

## Chart 3

```{r chart_3, echo=FALSE}

```

This chart shows ... We decided to go with a ... chart because ...

## Funding Over Time, by Source

This chart shows the relationship between Federal, State, and Local funding for the country over the years.
Blue represents Federal funding
Red represents State funding
Green represents Local funding

```{r chart_4, echo=FALSE}
generateTrends("data/funding/prepped/aggregate.csv")
```



